\textbf{ \Large{Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-03 Paper/PaperJahrSchlich.tex
Lab Ex überarbeitet

\todo{Abb}

@@

%
%In the present study, wireless sensor nodes of the type “Oracle Sun SPOTs” are used. The sensor nodes are Java-programmable enabling embedded analyses and the sensor nodes include a 3-dimensional accelerometer, temperature and other sensors (Oracle Lab, 2014). In this study, acceleration measurements taken from the structure are used for analyzing the structural condition. Furthermore, the radios of the sensor nodes ensure wireless communications between the sensor nodes as well as between the sensor nodes and the base station in order to transmit monitoring data or control commands. The base station is able to receive monitoring data measured by the sensor nodes, and the base station can store the data in a database installed on the local computer. The main Java classes are shown in an Unified Modelling Language diagram (UML diagram), which is a standard way to visualize the implementation of a application. The following UML diagrams (cp. Figure 1 and Figure 2) show just the main classes embedded into the base station and the sensor nodes. In the following subsection, the implementation of the main components of the fault detection strategy, including synchronization and fault detection, are shown.

@@

\textbf{2. paragraph: proposed nn}

\begin{itemize}
\item SNIPE? implementation in java?
\item activation function / identity function
\end{itemize}

\textbf{3. paragraph: learning general}

\begin{itemize}
\item set with test values
\item iterative weight adjustment
\end{itemize}

\textbf{4. paragraph?: learning, proposed}

@@

%\begin{itemize}
%\item test structure
%\item sensor installation
%\item type of excitation, acceleration is measured
%\end{itemize}

To validate the proposed approach, the SHM system is installed on a test structure in order to conduct laboratory experiments.
The test structure consists of four metal sheets with an area of 20\,cm by 60\,cm and 4\,mm of thickness.
Those metal sheets are mounted on threaded rods with a vertical clearance of approximately 40\,cm.
At the bottom, the threaded rods are fixed into a block of solid wood with an area of 40\,cm by 60\,cm and a height of 50\,cm.
The SHM system is installed onto the test structure by fastening a SunSPOT to each of the metal sheets.
The finished laboratory setup is shown in figure~\ref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}
The structure is excited by displacing one of the metal sheets to the side and releasing it.
This method of excitation ensures, that the structure vibrates in its Eigenfrequency with little interferences.

@@

\textbf{2. paragraph: data measurement and processing}

\begin{itemize}
\item learning phase
\item excitation
\item sensors start measuring
\item sensor nodes \textbf{perform fft} - what is fft
\item sensor nodes exchange frequencies
\item neural networks check integrity
\item if no faults detected, sensor nodes send data to basestation
\end{itemize}

\textbf{3. paragraph: sensor fault detection}

\begin{itemize}
\item simulation of sensor fault
\item neural networks check integrity -> error!
\item sensor node sends alert to basestation
\end{itemize}

@@

\section*{Notes}

package hyperref eingebunden: klickbare links, autoref

package SPOT in SensorNode umbenennen?!

citep, citet, see
%----------------------------------------------------------------------------------------

>>>>

@@

@@

%\textbf{2. paragraph: proposed nn}
%
%\begin{itemize}
%\item SNIPE? implementation in java?
%\item activation function / identity function
%\end{itemize}
%
%\textbf{3. paragraph: learning general}
%
%\begin{itemize}
%\item set with test values
%\item iterative weight adjustment
%\end{itemize}
%
%\textbf{4. paragraph?: learning, proposed}

@@

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure.
The test structure is a 4-story shear-frame consisting of four steel plates with an area of 25\,cm\,$\times$\,50\,cm and a thickness of 0.8\,mm.
Those plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom, the rods are fixed into a solid block of wood with an area of 40\,cm\,$\times$\,60\,cm and a height of 30\,cm.
The SHM system is installed on the test structure by fastening wireless sensor nodes to each story.
The laboratory setup is shown in \autoref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}

@@

The structure is excited by deflecting and releasing the top of the structure.
This excitation method ensures that the structure vibrates in a natural frequency with little interferences.
After excitation the sensor nodes automatically start measuring acceleration values with a sampling rate of 40\,Hz.
To minimize data traffic, each node performs a fast Fourier transform algorithm after sufficient acceleration samples have been collected.
%Generally FFTs are used to convert equidistant samples of a function into a combination of frequencies, and the corresponding magnitudes, that has the same sample values. 
The acceleration samples are converted into the vibration frequencies, and the corresponding magnitudes, of the building.
Each sensor node sends only the values of the predominating frequency, i.e. the frequency with the biggest magnitude.
The values are then stored in a MySQL database.

%\textbf{2. paragraph: data measurement and processing}
%
%\emph{\begin{itemize}
%\item learning phase
%\item excitation
%\item sensors start measuring
%\item sensor nodes \textbf{perform fft} - what is fft
%\item sensor nodes exchange frequencies
%\item neural networks check integrity
%\item if no faults detected, sensor nodes send data to basestation
%\end{itemize}}
%
%\textbf{3. paragraph: sensor fault detection}
%
%\begin{itemize}
%\item simulation of sensor fault
%\item neural networks check integrity -> error!
%\item sensor node sends alert to basestation
%\end{itemize}

@@
